Introductory statistics with `intRo`

### 2016-02-19 jcgs-paper-2016/paper.Rmd
Final changes

Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call `intRo`, available at http://www.intro-stats.com. `intRo` offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest in coding. Additionally, `intRo` stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text. The paper is structured as follows: section \ref{what-is-intro} introduces the application, its features and its usability. Section \ref{using-intro} describes the process of creating a classroom instance of `intRo` tailored to the individual instructor. Section \ref{understanding-intro} provides technical details on the implementation of `intRo`. Finally, Section \ref{conclusions-and-future-work} discusses some future possibilities and limitations of the software.

@@

@@

`intRo` can be downloaded, ran, and deployed on ShinyApps.io through the use of the R package `intRo`. Currently, the package is only available and GitHub, and can be installed using the devtools package as follows:

@@

## Modules
An `intRo` module is a set of self-contained executible R scripts that together produce a set of introductory statistics functionality. `intRo` modules were designed in this way to allow for simple dynamic creation of the user interface at run-time, as well as ease the process of converting existing analysis code to the `intRo` framework. In this section, we detail the structure of these modules, and the process of creating and deploying new modules.

>>>>

Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call `intRo`, available at http://www.intro-stats.com. `intRo` offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest in coding. Additionally, `intRo` stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text. The paper is structured as follows: section \ref{what-is-intro} introduces the application, its features and its usability. Section \ref{using-intro} describes the process of creating a classroom instance of `intRo` tailored to the individual instructor. Section \ref{understanding-intro} provides technical details on the implementation of `intRo`. Finally, section \ref{conclusions-and-future-work} discusses some future possibilities and limitations of the software.

@@

Although users can access intRo from \url{http://www.intro-stats.com}, course instructors may wish to customize their own instance.

@@

`intRo` can be downloaded, ran, and deployed on ShinyApps.io through the use of the R package `intRo`. Currently, the package is only available on GitHub, and can be installed using the devtools package as follows:

@@

To fully understand `intRo`, it is important to expand upon three underlying concepts. The first is the idea of modularity in the context of a Shiny application. The second is the idea of reproducibility in the context of a graphical user interface. Finally, the third is the idea of reactive programming in the context of a web application.

## Modules

An `intRo` module is a set of self-contained executible R scripts that together produce a set of introductory statistics functionality. `intRo` modules were designed in this way to allow for simple dynamic creation of the user interface at run-time, as well as ease the process of converting existing analysis code to the `intRo` framework. In this section, we detail the structure of these modules, and the process of creating and deploying new modules.
